On the combination of Set Functions and Failures

### 2013-04-15 docs/src/manual.tex
Manual update (:set prompt added)

>>>>

\item[\fbox{\code{prompt $p$}}]\pindex{prompt}
Sets the user prompt which is shown when \CYS is waiting for input.
If the parameter $p$ starts with a letter or a percent sign,
the prompt is printed as the given parameter,
where the sequence \ccode{\%s} is expanded to the list of
currently loaded modules
and \ccode{\%\%} is expanded to a percent sign.
If the prompt starts with a double quote, it is read as a string and,
therefore, also supports the normal escape sequences that can occur
in Curry programs. The default setting is
\begin{curry}
:set prompt "%s> "
\end{curry}
